---
title: Sentiment Report
author: Saptarshi Guha <joy@mozilla.com>
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
 html_document:
    mathjax: default
    self_contained: false
    theme: readable
    highlight: haddock
    number_sections: false
    code_folding: show
    toc: false
    toc_depth: 3
---


```{r child = '/home/sguha/mz/template2.Rmd'}
```




An example of literate coding for a production report. 


# Configuration

Always run

```{r child='./options.Rmd'}
```


## Library Functions

Load all library functions. For obvious reasons, needs to be run before others.


```{r child = './library.Rmd'}
```



## Regular Cron Job

This file is  rendered every day (or on some regular basis)

```{r child = './cron.Rmd'}
```


## Back Fill 

One time. Currently I have run it from 2017-11-01 till 2018-03-14.

```{r child = './backfill.Rmd'}
```


# About {-}

For nearly four plus years, we are at mozilla have been looking for a way to
gauge the user sentiment towards Firefox. With Shield and Unified Telemetry,
we are almost there. The document below is inspired by the ideas of "literate
coding" : code and elaboration in the same document. With RMarkdown and the
appropriate libraries this can be run from the R console to produce this web
page.

We ask 1% of our users, every day, two questions

- Would you recommend Firefox to a friend or family member?
- Will you keep using Firefox in the future?

which are growth and retention questions. We also plan to include some other
questions too. These two questions are shown to everyone in the 1% sample(it's opt out) and
though we have some response bias , it is not much. Background work can be found  at

- https://metrics.mozilla.com/protected/sguha/sentiment/56/index.html
- https://metrics.mozilla.com/protected/sguha/sentiment/57/index.html
- https://metrics.mozilla.com/protected/sguha/sentiment/58/index.html

A background to this document can be found [here](https://docs.google.com/document/d/1cgKWaU__4b96w0ZjuX9W9G4lq6VWbgHXkD33BO3XA4k/edit)
# Files on S3

```{r child = './files.Rmd'}
```

